\ttlfnt{Comparing the performance of websites and their content distribution networks}

### 2016-08-28 Writeup/paper.tex
Some minor edits

Of the video streaming services on the internet, YouTube is most popular with over a billion users \cite{youtubeStats}. Everyday, YouTube generates billions of views with people watching hundreds of million of hours of content \cite{youtubeStats}. With new content constantly getting generated around the world, caching strategies are required so that this content can be served up at a high throughput from as close as possible to the user. ISPs play a critical role in this through their peering policies and by providing their own CDNs for various content \cite{Labovitz:2010:IIT:2043164.1851194}.

Our aim in this paper is to investigate the performance of the CDN's that serve this content. We will examine different streaming services across a variety of South African Internet Service Providers (ISP) to examine how traffic is routed and where it comes from. In addition, we will also examine the caching behaviour of YouTube, which has local caches in South Africa. We have developed a tool which automates many of the aforementioned measurements. It can take a list of URLs to content on a streaming service and record various performance metrics regarding how the content is delivered to the end-user.

Section \ref{sec:related} will examine related work in measuring the performance of streaming services and studies which investigate the behaviour of CDNs for multimedia streaming services. Section \ref{sec:method} describes the tool that we developed and details the steps we followed in using it to capture our results. Section \ref{sec:results} presents the results and a discussion thereof.

\section{Related Work}\label{sec:related}
% Relevant work that has been done
There have been a number of studies on how the performance of video streaming affects the quality of experience (QoE) for the user. Casas \textit{et al.} \cite{6975242} took an ISP traffic view by analysing 1 months worth of YouTube packet flows from a large European ISP. The study challenges Google's Video Quality Report\footnote{http://www.google.com/get/videoqualityreport/} as it only considers ISP and access link bottlenecks as the root cause of bad user experience \cite{6975242}. Casas \textit{et al.} \cite{6975242} presents how poor content server selection by Google resulted in a large scale reduction for in QoE for many YouTube users. Fiadino \textit{et al.} \cite{6932930} developed an tool for ISP's to detect unexpected cache-selection events and changes in the traffic delivered by CDNs. Anomalous CDN behaviour has been shown to have a large impact for ISP's carrying the traffic and end-users \cite{6932930, Plissonneau:2012:LVH:2155555.2155588}. Zhu \textit{et al.} \cite{6233056} developed LatLong, a tool for CDN's to diagnose large latency increases on the network through passive measurement of traffic and routing. Results from analysing a one month's data from Google's CDN show that more than 40\% of latency increases coincide with interdomain routing changes and more than one-third involve a shift in traffic to different servers. Juluri \textit{et al.} \cite{6038496} developed Pytomo, a tool to measure playback quality on an end-host. The tool captures various metrics such as delay towards the server, download rates and buffering duration \cite{6038496}. These can then be used to measure Quality of Experience.

@@

To measure the performance of CDNs, we have created a tool to automatically capture various quantitative and qualitative performance metrics when given a list of URLs to online video or audio content. In order to compare the performance of CDNs to that of the websites that present the content, we measure 2 primary quantitative metrics: Ping or Round-trip-time and the number of hops required to reach the server. We also measure the throughput to the CDN. To gain further insight into the potential causes for variances in performance, we also take note of the location and hosting organisation of the web page and CDN IPs. The source code for our tool is publicly available on GitHub\footnote{CDNPerf -  https://github.com/jacquesh/cdnperf}.

@@

\subsubsection{Discussions}
Being a significantly higher-bandwidth connection than what is available to a home user, this test over UCT's network makes the effects of caching and performance of CDNs more pronounced. Note the difference in throughput for the unpopular Youtube video on the first run to the second and third runs. On run 1 the video is not cached (as is evident by the higher RTT) and is delivered at a bitrate far below what the connection supports. On the run 2 the video has been cached and is delivered with a significantly higher throughput. What is interesting to note however, is that on run 3 the throughput is again significantly higher than run 2, even though the RTT to the server that delivers it has not changed. This suggests that the cache considers it to be ``hotter'' because of the additional request for it, and serves it at a higher throughput. Another possibility is that while video is available at the server, the caching process has not fully completed, leading to slower throughput on run 2. The aforementioned behaviour were found to hold true for subsequent tests on other unpopular YouTube videos, not depicted in this paper.

Another interesting point to make is that the throughput recorded for Twitch.tv is actually significantly higher than that of Youtube, even for very popular videos. This is surprising since the Twitch.tv content is not being delivered from a server residing on the African continent, while the popular Youtube content is being delivered from caches within Cape Town.

>>>>

Of the video streaming services on the internet, YouTube is most popular with over a billion users \cite{youtubeStats}. Everyday, YouTube generates billions of views with people watching hundreds of million of hours of content \cite{youtubeStats}. With new content constantly getting generated around the world, caching strategies are required so that this content can be served up at a high throughput from as close as possible to the user. Internet Service Providers (ISPs) play a critical role in this through their peering policies and by providing their own CDNs for various content \cite{Labovitz:2010:IIT:2043164.1851194}.

Our aim in this paper is to investigate the performance of the CDN's that serve this content. We will examine different streaming services across a variety of South African ISPs to examine how traffic is routed and where it comes from. In addition, we will also examine the caching behaviour of YouTube, which has local caches in South Africa. We have developed a tool which automates many of the aforementioned measurements. It can take a list of URLs to content on a streaming service and record various performance metrics regarding how the content is delivered to the end-user.

Section \ref{sec:related} will examine related work in measuring the performance of streaming services and studies which investigate the behaviour of CDNs for multimedia streaming services. Section \ref{sec:method} describes the tool that we developed and details the steps we followed in using it to capture our results. Section \ref{sec:results} presents the results and discussions thereof.

\section{Related Work}\label{sec:related}
% Relevant work that has been done
There have been a number of studies on how the performance of video streaming affects the quality of experience (QoE) for the user. Casas \textit{et al.} \cite{6975242} took an ISP traffic view by analysing 1 month's worth of YouTube packet flows from a large European ISP. The study challenges Google's Video Quality Report\footnote{http://www.google.com/get/videoqualityreport/} as it only considers ISP and access link bottlenecks as the root cause of bad user experience \cite{6975242}. Casas \textit{et al.} \cite{6975242} presents how poor content server selection by Google resulted in a large scale reduction for in QoE for many YouTube users. Fiadino \textit{et al.} \cite{6932930} developed a tool for ISPs to detect unexpected cache-selection events and changes in the traffic delivered by CDNs. Anomalous CDN behaviour has been shown to have a large impact for ISPs carrying the traffic and end-users \cite{6932930, Plissonneau:2012:LVH:2155555.2155588}. Zhu \textit{et al.} \cite{6233056} developed LatLong, a tool for CDNs to diagnose large latency increases on the network through passive measurement of traffic and routing. Results from analysing a one month's data from Google's CDN show that more than 40\% of latency increases coincide with interdomain routing changes and more than one-third involve a shift in traffic to different servers. Juluri \textit{et al.} \cite{6038496} developed Pytomo, a tool to measure playback quality on an end-host. The tool captures various metrics such as delay towards the server, download rates and buffering duration \cite{6038496}. These can then be used to measure Quality of Experience.

@@

To measure the performance of CDNs, we have created a tool to automatically capture various quantitative and qualitative performance metrics when given a list of URLs to online video or audio content. In order to compare the performance of CDNs to that of the websites that present the content, we measure 2 primary quantitative metrics: Ping or Round-trip-time and the number of hops required to reach the server. We also measure the throughput to the CDN. To gain further insight into the potential causes for variances in performance, we also take note of the location and hosting organisation of the web page and CDN IPs as well as the IP which the content was actually delivered from. The source code for our tool is publicly available on GitHub\footnote{CDNPerf -  https://github.com/jacquesh/cdnperf}.

@@

\subsubsection{Discussions}
Being a significantly higher-bandwidth connection than what is available to a home user, this test over UCT's network makes the effects of caching and performance of CDNs more pronounced. Note the difference in throughput for the unpopular Youtube video on the first run to the second and third runs. On run 1 the video is not cached (as is evident by the higher RTT) and is delivered at a bitrate far below what the connection supports. On the run 2 the video has been cached and is delivered with a significantly higher throughput. What is interesting to note however, is that on run 3 the throughput is again significantly higher than run 2, even though the RTT to the server that delivers it has not changed. This suggests that the cache considers it to be ``hotter'' because of the additional request for it, and serves it at a higher throughput. Another possibility is that while video is available at the server, the caching process has not fully completed, leading to slower throughput on run 2. This behaviour was repeated in subsequent tests on other unpopular YouTube videos. For brevity we have not included the results of the additional tests in this paper.

Another trend to take note of is that the throughput recorded for Twitch.tv is actually significantly higher than that of Youtube, even for very popular videos. This is surprising since the Twitch.tv content is not being delivered from a server residing on the African continent, while the popular Youtube content is being delivered from caches within Cape Town.
